\documentclass{article} % For LaTeX2e
\usepackage{nips13submit_e,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[ruled,vlined]{algorithm2e}
%\documentstyle[nips13submit_09,times,art10]{article} % For LaTeX 2.09


\title{Predicting Popularity of YouTube Video}

\author{
Loc Do \\
Heinz College,
Carnegie Mellon University \\
Pittsburgh PA, 15213\\
\texttt{halocd@andrew.cmu.edu} \\
\And
Joseph Richardson \\
School of Computer Science,
Carnegie Mellon University \\
Pittsburgh PA, 15213 \\
\texttt{jmrichar@andrew.cmu.edu} \\
}

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\nipsfinalcopy % Uncomment for camera-ready version

\begin{document}

\maketitle

\begin{abstract}
	In this work we address the problem of ranking two objects given their features. The problem is applied to a context of guessing the more popular of two given YouTube videos. We formulate this problem into two different approaches, namely binary classification and linear regression. Experiments are conducted in our data set crawled from YouTube over a one-month span. Results show that both approaches yield a slightly above 50\% accuracy. We conclude that bag-of-words features with linear classifiers are not efficient in determining videos' popularity.
\end{abstract}

\section{Introduction}
\label{sec:intro}
	YouTube is one of the most popular video-sharing online platform on the Internet. It attracts billions of unique users visit monthly and had content for a wide variety of topics. YouTube users can earn money from the number of views of their uploaded videos. Hence, understanding the secrets of making a popular YouTube video is essential for people who want to use YouTube professionally. There are many factors to determine popularity of a video, but in general we can reduce them down to having good content and a good marketing plan. One of the techniques to attract more views is to make the video's "visual appearance" look appealing via catchy keywords, informative cover picture, etc.

	The ranking problem (aka. Learning to rank\footnote{http://en.wikipedia.org/wiki/Learning\_to\_rank}) is a typical supervised learning problem of predicting the rank of a set of items regarding some set of criteria. It has a numerous applications in a broad number of domains such as web search, multimedia retrieval, recommender systems, etc. Results from such problems can bring benefits to Internet users, such as saving their time by introducing only the content most relevant to their interests. In YouTube context, ranking problems arise in recommending the most relevant videos to a given video. Another application is to rank video popularity overall.

	\textbf{Problem statement.} Given a set of videos, each is associated with a set of bag-of-words and numeric features extracted from their metadata. We use the number of views as our measure of popularity. Given two videos with their features, the video ranking problem is to construct a model to accurately predict which one has more views.  In order to do this, we approach the problem in two different manners:  Ranking by classification, and ranking by regression.

\section{Ranking by Classification}
\label{sec:ranking}
	\input{sec_ranking}
\section{Ranking by Regression}
\label{sec:regression}
	\input{sec_regression}
\section{Experimental study}
\label{sec:experiment}
	\input{sec_experiments}
\subsection{Results}
\label{sec:results}
	\input{sec_results}
\section{Related work}
\label{sec:related}
	\input{sec_related}

\section{Conclusion}
Two simple linear approaches, classification and regression, are explored in a context of predicting videos having more view counts. Two types of features are extracted, namely bag-of-words (from videos' title) and numeric features (video's metadata). The slightly above 50\% accuracy shows that the features/approaches we selected are not indicative enough to separate the cases.  Of our two main method types, classification performed consistently better.

As for future work, there are a few things we would like to do. First, we want to try out more complicated approaches (e.g. non-linear), such as AdaRank, SVMRank, Gaussian Processes etc. Secondly, we may need to extract more indicative features by exploiting the videos' comments. Thirdly, we want to experiment on all bins, not limited to the first 30 bins.

\section*{Acknowledgments}
	Our sincere thanks to Anthony for his patience and valuable inputs to improve our project.

\section*{References}
\label{sec:references}
	\input{sec_references}

\end{document}
